---
title: "Aboriginal Australia 1970-1979"
author: "Matti Munk Nielsen"
date: "11 May 2024"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Download

## Library
```{r}
library(tidyverse)
library(tidytext)
library(ggwordcloud)
```

## Read the csv.file
```{r}
Aboriginal_1970_1979 <- read_csv("Aboriginal_Australia_1970-1979.csv")

```
## Show csv.file
```{r}
Aboriginal_1970_1979
```
# Textmining

## Unnest tokens
Unnest tokens separates individual words from the articles in a column.
```{r}
Aboriginal_1970_1979_tokens <-Aboriginal_1970_1979 %>%
  unnest_tokens(word,article_text)

Aboriginal_1970_1979_tokens
```

## Count words
```{r}
Aboriginal_1970_1979_wc <- Aboriginal_1970_1979_tokens%>%
  count(word)%>%
  arrange(-n)

Aboriginal_1970_1979_wc
```

## Stopwordslist
A stopwordslist is a list of all the stopwords in all the 100 articles.
```{r}
Aboriginal_1970_1979_wc
```


## Remove stopwordslist
```{r}
Aboriginal_1970_1979_stop <- Aboriginal_1970_1979_tokens%>%
  anti_join(stop_words)

Aboriginal_1970_1979_stop
```

## Count words again
```{r}
Aboriginal_1970_1979_swc <- Aboriginal_1970_1979_stop%>%
  count(word)%>%
  arrange(-n)

Aboriginal_1970_1979_swc
```

## Show Aboriginal 1970 to 1979 swc Head
```{r}
 Aboriginal_1970_1979_swc%>%
  head(10)
```


## Remove nontext
```{r}
Aboriginal_1970_1979_no_numeric <- Aboriginal_1970_1979_stop%>%
  filter(is.na(as.numeric(word)))
```
## View nontext
```{r}
Aboriginal_1970_1979_no_numeric
```


## Unique words
Length counts the rare words in the articles.
```{r}
length(unique(Aboriginal_1970_1979_no_numeric$word))
```

## Top 100 words
Show the 100 most used words in all the 100 articles.
```{r}
Aboriginal_1970_1979_top100 <- Aboriginal_1970_1979_no_numeric%>%
  count(word)%>%
  arrange(-n)%>%
  head(100)

Aboriginal_1970_1979_top100
```

## Cloud
```{r}
Aboriginal_1970_1979_cloud <- ggplot(data = Aboriginal_1970_1979_top100, aes( label = word)) + geom_text_wordcloud() + theme_minimal()

Aboriginal_1970_1979_cloud
```


## Customize cloud
Shows the most frequent used words from the 100 articles where green is most,then yellow and last pink.
```{r}
ggplot(data = Aboriginal_1970_1979_top100, aes(label = word, size = n)) + 
  geom_text_wordcloud_area(aes(color = n), shape = "diamond") +
  scale_size_area(max_size = 12) +
  scale_color_gradientn(colors = c("pink", "yellow", "green")) +
  theme_minimal()

```

# Sentiment analysis

## Lexicon afinn
```{r}
get_sentiments(lexicon = "afinn")
```


```{r}
afinn_pos <- get_sentiments("afinn") %>%
  filter(value %in% c(3,4,5))
```


```{r}
afinn_pos
```


## Lexicon bing
```{r}
get_sentiments(lexicon = "bing")

```

## Lexicon nrc
```{r}
get_sentiments(lexicon = "nrc")
```


## Aboriginal 1970 to 1979 afinn
Inner join connects the stopwords column(word) with the afinn column(value).
```{r}
Aboriginal_1970_1979_afinn <-  Aboriginal_1970_1979_stop%>% 
  inner_join(get_sentiments("afinn"))

Aboriginal_1970_1979_afinn
```
## Aboriginal 1970 to 1979 afinn hist
Counts the value of Aboriginal 1970 to 1979 afinn.
```{r}
Aboriginal_1970_1979_afinn_hist <- Aboriginal_1970_1979_afinn%>% 
  count(value)

Aboriginal_1970_1979_afinn_hist
```

## Plot Aboriginal 1970 to 1979 afinn hist
The x-axis(value) is the sentiment value where negative is shown as minus and positive with no minus and n is the amount of words that has the specific sentiment value from the x-axis(value).
```{r}
ggplot(data = Aboriginal_1970_1979_afinn_hist, aes(x = value, y = n)) + 
  geom_col()
```


## Aboriginal 1970 to 1979 afinn2
Here filter removes words that do not have a value on 2.
```{r}
Aboriginal_1970_1979_afinn2 <- Aboriginal_1970_1979_afinn %>% 
  filter(value == 2)
```

## Unique 2 words score
Shows how unique each word is with 1 being the highest.
```{r}
unique(Aboriginal_1970_1979_afinn2$word)
```


## Count plot Aboriginal 1970 til 1979 afinn2 n
```{r}
Aboriginal_1970_1979_afinn2_n<- Aboriginal_1970_1979_afinn2%>% 
  count(word, sort = TRUE) %>% 
  mutate(word = fct_reorder(factor(word), n))

Aboriginal_1970_1979_afinn2_n
```
 
## Count and plot graph
The y-axis are words while the x-axis(n) is the amount of positivity in a word from the y-axis.
```{r}
ggplot(data = Aboriginal_1970_1979_afinn2_n, aes(x = word, y = n)) +
  geom_col() +
  coord_flip()
```


## Summerize sentiment
```{r}
Aboriginal_1970_1979_summery <- Aboriginal_1970_1979_afinn%>% 
  summarise(mean_score = mean(value), median_score = median(value))

Aboriginal_1970_1979_summery
```


## Aboriginal 1970 til 1979 nrc
Inner join connects the stopwords column(word) with the nrc column(sentiment).
```{r}
Aboriginal_1970_1979_nrc <- Aboriginal_1970_1979_stop%>% 
  inner_join(get_sentiments("nrc"))
```


## Exclude
Anti join finds all words that do not match two dataframes.
```{r}
Aboriginal_1970_1979_exclude <- Aboriginal_1970_1979_stop %>% 
  anti_join(get_sentiments("nrc"))

Aboriginal_1970_1979_exclude
```

## Count most exluded
```{r}
Aboriginal_1970_1979_exclude_n <-  Aboriginal_1970_1979_exclude%>% 
  count(word, sort = TRUE)

Aboriginal_1970_1979_exclude_n
```

## Show Aboriginal 1970 to 1979 exclude n head
```{r}
head(Aboriginal_1970_1979_exclude_n)
```


## Emplot Aboriginal 1970 to 1979 nrc n
The x-axis(sentiment) is the type of sentiment while the y-axis(n) is the amount of a sentiment from the x-axis.
```{r}
Aboriginal_1970_1979_nrc_n <- Aboriginal_1970_1979_nrc %>% 
  count(sentiment, sort = TRUE )

ggplot(data = Aboriginal_1970_1979_nrc_n, aes(x = sentiment, y = n)) +
  geom_col()
```


## Count sentiment and word
There are multiple graphs each divided by a sentiment and each have a x-axis which represents the amount of sentiment to a specific word from the y-axis.
```{r}
Aboriginal_1970_1979_nrc_n5 <- Aboriginal_1970_1979_nrc %>% 
  count(word,sentiment,sort = TRUE) %>% 
  group_by(sentiment) %>% 
  top_n(5) %>% 
  ungroup()

Aboriginal_1970_1979_nrc_gg <- ggplot(data = Aboriginal_1970_1979_nrc_n5, aes(x = reorder(word,n), y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, ncol = 2, scales = "free") +
  coord_flip() +
  theme_minimal() +
  labs(x = "word" , y = "count")

Aboriginal_1970_1979_nrc_gg
```


## Save it
```{r}
ggsave(plot = Aboriginal_1970_1979_nrc_gg,
       filename ="figures/ipcc_nrc_sentiment.png", 
      height = 8,
      width = 5)

```

